PhD Research Proposal: Molecular Level Design of Nanoporous Lyotropic Liquid Crystal Membranes for Aqueous Separations \\ \vspace{0.5cm} \large Advisors: Michael Shirts and Richard Noble

### 2019-05-13 Ben_Manuscripts/comps/Draft.tex
comments on the tex

  More highly selective nanoporous membranes would be useful for 
  performing complex aqueous separations with seawater and various
  types of wastewater. For example, sodium chloride and boron in seawater 
  \cite{fritzmann_state---art_2007} and organic micropollutants found in
  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
  represent a small subset of the diverse contaminants of water sources. 
  By efficiently separating contaminants from feed solutions with
  highly selective membranes, it is possible to reduce the number of 
  required membrane passes and post-treatment steps needed for a given 
  filtration process \cite{werber_materials_2016}, thus lowering energy 
  requirements and cost. Additionally, one can extract valuable 
  resources from the feed streams. For example, flowback water produced 
  during hydraulic fracturing of shale formations contains dissolved 
  species like acetate whose extraction has economic value \cite{dischinger_application_2017}.

@@

  The downfall of RO and NF membranes can be summarized by the well-known
  permeability-selectivity tradeoff. Namely, it is difficult to increase the
  permeability of a desired molecular or atomic species, while maintaining
  the same retention of an undesired species.\cite{werber_materials_2016}

@@

  Ultrathin-film graphene and graphene oxide membranes are a very active
  area of research because they offer potential for extremely high 
  permeability membranes. An ideal graphene membrane is a 2D material 
  composed of a single layer of graphene.\cite{humplik_nanostructured_2011}
  Synthesis of a single layer of graphene at a large scale without introducing
  defects is a challenge that has not yet been overcome. Multilayered graphene
  membranes are potentially easier to synthesize and more scalable which has 
  resulted in an increasing interest over recent years.\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}

@@

  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
  (LLC) membranes can be produced at moderate scale and may be capable of 
  performing highly selective separations. LLCs are amphiphilic molecules 
  that have the ability to self-assemble into porous nanostructures~\cite{smith_ordered_1997}
  that can be cross-linked to create mechanically strong membrane films with 
  periodic uniform-sized pores on the order of 1 nm in diameter~\cite{zhou_supported_2005}. 
  Since LLC polymer membranes lack an appreciable pore size distribution, they 
  inherently exhibit high selectivity due to their molecular weight cut-off 
  (MWCO)~\cite{zhou_supported_2005}. Additionally, LLC monomers can be salts,
  and therefore lead to Donnan exclusion of ions at the membrane-feed solution 
  interface.\cite{donnan_theory_1995}
%    The membrane gains a net surface charge when counterions from
%  the head groups that line the pore walls escape into the feed solution in an
%  effort to balance the gradients of concentration and electric potential
%  \cite{donnan_theory_1995}.

@@

  \noindent There are four primary objectives of this PhD research.
  \begin{enumerate}

@@

    %MRS: probably should talk about this 1) with proper tense (some of these things have been done) and 2) talk about what YOU are doing, not we. I helped design the research, but you carried essentially all of it out! If phrased in future tense, committee will be confused, thinking those are things still to be done.

    A useful molecular-level model should incorporate a detailed picture 
    of the nanoscopic pore structure, which is crucial to understanding
    the role of monomer structure in solute transport and membrane design.
    I have created a maximally consistent structural model by comparing 
    simulated X-ray diffraction (XRD) patterns, generated from MD trajectories,
    to an experimental 2D wide angle X-ray scattering (WAXS) spectrum of a 
    Col\textsubscript{h} phase LLC membrane. I have used this model as an 
    example in order to understand the ease with which we can apply our approach
    to alternate monomers and other LC phases.

@@

  \textbf{\large Objective 1:} {\large Build and understand the nanoscopic structure
  of the H\textsubscript{II} phase} (\textcolor{green!40!olive}{\textbf{Complete}})

  My first task was to develop a procedure for building and equilibrating 
  an atomistic LLC membrane system (see Figure~\ref{fig:assembly}). I chose to build
  a monoclinic unit cell consisting of four pores. Each pore is composed of monomer
  columns, where each column consists of 20 monomers stacked on top of each other
  so that the phenyl groups are coplanar with each other and the $xy$ plane. The
  columns are oriented so that the hydrophilic monomer head groups face towards
  the pore center. I did not add any water to the initial configuration because I
  compared the structure to experimental data for a system claimed to be
  synthesized with only neat monomer. I equilibrated unit cells using a series
  of simulations with head groups held in place by position restraints, gradually
  reducing the force constant of the position restraints until the system
  was completely unrestrained. I let the system equilibrate for 400 ns of simulation
  time.

  \begin{figure}[!htb]
      \centering
      \begin{subfigure}{.325\textwidth}
              \centering
              \vspace{0.5cm}
              \includegraphics[width=\textwidth]{NaGA3C11_wedge.eps}
              \vspace{0.05cm}
              \caption{}~\label{fig:monomer}
      \end{subfigure}
%      \begin{subfigure}{.3\textwidth}
%              \centering
%              \includegraphics[width=\textwidth]{monomer_twocolor.pdf}
%              \caption{}~\label{fig:atomistic_monomer}
%      \end{subfigure}
%      \begin{subfigure}{0.3\linewidth}
%              \centering
%              \includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
%              \caption{}~\label{fig:wedge}
%      \end{subfigure}
              \begin{subfigure}{0.325\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{columns.pdf}
              \caption{}~\label{fig:wedge_layer}
      \end{subfigure}
      \begin{subfigure}{0.325\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
              \caption{}~\label{fig:hex_packing_simple}
      \end{subfigure}
      \caption{(a) The LLC monomer Na-GA3C11 exhibits wedge-like character. (b) 
      Monomers stack on top of each other to create columns with short range order,
      then assemble into pores with hydrophilic head groups (blue) facing towards 
      the pore center. (c) The pores assemble into hexagonally packed columnar
      mesophases.}~\label{fig:assembly}
      \vspace{-0.5cm}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  %BJC: probably change this legend to `d = x Angstroms` instead of 
  % disordered/ordered, since I don't have space to talk about ordered / disorderd configurations (requires 
  % nematic order parameter to give a complete justification of the names)
  \includegraphics[width=\textwidth]{regional_density_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.pdf}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.pdf}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.pdf}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  \caption{In all systems studied, the component radial distribution functions are similar.
      They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
          regions. The biggest differences are at r=0 where noise is higher due to
          decreased sampling. The center of the pore is not hollow, but contains sodium ions and
          head groups, even when the system is solvated. This architecture may impede transport in
          the real system in a chemically-dependent manner.
          The solvated system has a lower density of head groups near the
          pore center which is likely due to the swelling that is necessary in order to fit water
          molecules in the pore region.}~\label{fig:overlaid_densities}
  \vspace{-0.5cm}
  \end{figure}

  \noindent \textbf{\large Objective 2:} \textit{\large Determine transport mechanisms} (\textcolor{green!40!olive}{\textbf{Complete}})

@@

  \begin{wrapfigure}{l}{0.65\textwidth}
  \centering
  \vspace{-0.4cm}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{component_density_dry.pdf}
%  %BJC: simulation is extended to smooth out these curves
%  \caption{Dry System}\label{fig:component_density_dry}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \vspace{-0.5cm}
%  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
%  \label{fig:monomer_color_coded}
%  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. The monomer groups labeled in each plot correspond to
  the color-coded monomer pictured in Figure~\ref{fig:HII_mon}. All RDFs
  represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin to which they belong. The black
  dashed lines are positioned so that they intersect with the maximum head group
  density. (a) In the 5 wt \% system, monomer head groups are situated about 0.45 nm
  from the pore center. Sodium and water are densest near the pore center 
  (b) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
  for more water. Water is densest at the pore center, but sodium ion density
  peaks closer to the head groups since many stay bound to carboxylate groups.}\label{fig:component_densities}
  \vspace{-0.75cm}
  \end{wrapfigure}

@@

  The pores of the H\textsubscript{II} phase are primarily a mixture of 
  water and sodium ions. The maximum density of head groups occurs 0.45
  and 0.65 nm from the pore center in the 5 and 10 wt\% water systems 
  respectively (see Figure~\ref{fig:component_densities}). There are 
  almost no head groups occupying the pore center.

@@

  % BJC: do you think I can get away with an appendix with the solute table + abbreviations that
  % doesn't count towards the page limit?
  We observed transport of 20 different small polar solutes in the pores of
  our model. We created a separate initial configuration for each solute 
  studied and placed 6 solutes, equally spaced in $z$, in each nanopore.
  After a 5 ns equilibration, we allowed the solutes to simulate for
  1 microsecond.

@@

  I have developed a procedure that can build both Ia3d and Pn3m unit cells.
  To our knowledge, nobody has ever built an atomistic bicontinuous cubic 
  phase system without the aid of self-assembly. Self-assembly can be a long
  process, especially for fully atomistic systems. Instead, we used known
  analytical equations that describe the surface of these systems in order 
  to place monomers into a unit cell. Monomers are placed perpendicular to
  the surface in random locations that don't overlap. One can control the 
  pore size by translating monomers perpendicular to the surface at the 
  point where they are attached.

@@

%BJC: not sure how much more detail to include. Can go into a lot. Have to expand box and slowly compress. Add glycerol iteratively until there are no gaps.

>>>>

  More highly selective nanoporous membranes would be useful for 
  performing complex aqueous separations with seawater and various
  types of wastewater. For example, sodium chloride and boron in seawater 
  \cite{fritzmann_state---art_2007} and organic micropollutants found in
  municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006}
  %MRS2: rephrase; sound like you are talking about only a minor problem.  I would suggest adding a few more with citations
  %MRS2: to show you are aware of the breadth of the subject, and these aren't the only ones you know about.
  %represent a small subset 
  are only a few 
  of the diverse contaminants of water sources. 
  By efficiently separating contaminants from feed solutions with
  highly selective membranes, it is possible to reduce the number of 
  required membrane passes and post-treatment steps needed for a given 
  filtration process \cite{werber_materials_2016}, thus lowering energy 
  requirements and cost. Additionally, one can extract valuable 
  resources from the feed streams. For example, flowback water produced 
  during hydraulic fracturing of shale formations contains dissolved 
  species like acetate whose extraction has economic value \cite{dischinger_application_2017}.

@@

  The downfall of RO and NF membranes can be summarized by the well-known
  permeability-selectivity tradeoff. Namely, it is difficult to increase the
  permeability of a desired molecular or atomic species, while maintaining
  the same retention of 
  %MRS2: an undesired, or all of the undesired?
an undesired species.\cite{werber_materials_2016}

@@

  %MRS2: this section is not so useful, becaue it talks about things you are NOT doing.  In a dissertation, would be good 
  %MRS2: context, but here, it distracts a bit because it's not summarizing what you are presenting in this paper. i.e. with 15 pages, you don't want to spend space talking about what you aren't doing.  Ideally, cut down to 1 paragraph just to
  %MRS2: show that you are aware of existing technologies.
  Ultrathin-film graphene and graphene oxide membranes are a very active
  area of research because they offer potential for extremely high 
  permeability membranes. An ideal graphene membrane is a 2D material 
  composed of a single layer of graphene.\cite{humplik_nanostructured_2011}
  Synthesis of a single layer of graphene at a large scale without introducing
  defects is a challenge that has not yet been overcome. Multilayered graphene
  membranes are potentially easier to synthesize and more scalable which has 
  resulted in an increasing interest over recent years.\cite{cohen-tanugi_multilayer_2016,wei_multilayered_2018}

@@

  Preliminary evidence has shown that cross-linked lyotropic liquid crystal
  (LLC) membranes can be produced at moderate scale and may be capable of 
  performing highly selective separations. 
  %MRS2: should be a citation here since you make specific claims.
  LLCs are amphiphilic molecules 
  that have the ability to self-assemble into porous nanostructures~\cite{smith_ordered_1997}
  that can be cross-linked to create mechanically strong membrane films with 
  periodic uniform-sized pores on the order of 1 nm in diameter~\cite{zhou_supported_2005}. 
  Since LLC polymer membranes 
  %MRS2: making a positive statement rather than negative, clearer
  %lack an appreciable 
  have a very narrrow
  pore size distribution, they 
  inherently exhibit high selectivity due to their molecular weight cut-off 
  (MWCO)~\cite{zhou_supported_2005}. Additionally, LLC monomers can be salts,
  and therefore lead to Donnan exclusion of ions at the membrane-feed solution 
  interface.\cite{donnan_theory_1995}
%    The membrane gains a net surface charge when counterions from
%  the head groups that line the pore walls escape into the feed solution in an
%  effort to balance the gradients of concentration and electric potential
%  \cite{donnan_theory_1995}.

@@

  \noindent There are four primary objectives of this PhD research.
%MRS2: Explicitly state here that the first two objectives are completed, and that the others are underway.
  \begin{enumerate}

@@

    %MRS: probably should talk about this 1) with proper tense (some of these things have been done) and 2) talk about what YOU are doing, not we. I helped design the research, but you carried essentially all of it out! If phrased in future tense, committee will be confused, thinking those are things still to be done.  
    %MRS2: Objectives shouldn't include a description of what has and hasn't been done.  Then it's not an really just an objective anymore.  I would suggest rephrasing these in terms of the intellectual objective, focusing on the questions to be asked and hypotheses to be tested, and then talk in the next section about what has been done (or is to do).

    A useful molecular-level model should incorporate a detailed picture 
    of the nanoscopic pore structure, which is crucial to understanding
    the role of monomer structure in solute transport and membrane design.
    I have created a maximally consistent structural model by comparing 
    simulated X-ray diffraction (XRD) patterns, generated from MD trajectories,
    to an experimental 2D wide angle X-ray scattering (WAXS) spectrum of a 
    Col\textsubscript{h} phase LLC membrane. I have used this model as an 
    example in order to 
    %MRS2: I don't know that it's easy yet . . . 
    %understand the ease with which 
    demonstrate how 
    we can apply our approach
    to alternate monomers and other LC phases.

@@

  \textbf{\large Objective 1:} {\large Build and understand the nanoscopic structure
  of the H\textsubscript{II} phase} (\textcolor{green!40!olive}{\textbf{Complete}})
  %MRS2: provide paper citation here, rather than at end of section.

  My first task was to develop a procedure for building and equilibrating 
  an atomistic LLC membrane system (see Figure~\ref{fig:assembly}). I chose to build
  a monoclinic unit cell consisting of four pores. Each pore is composed of monomer
  columns, where each column consists of 20 monomers stacked on top of each other
  so that the phenyl groups are coplanar with each other and the $xy$ plane. The
  columns are oriented so that the hydrophilic monomer head groups face towards
  the pore center. I did not add any water to the initial configuration because I
  compared the structure to experimental data for a system claimed to be
  synthesized with only neat monomer. I equilibrated unit cells using a series
  of simulations with head groups held in place by position restraints, gradually
  reducing the force constant of the position restraints until the system
  was completely unrestrained. I let the system equilibrate for 400 ns of simulation
  time.
  %MRS2: above: less detail on what you did (for example, 400 ns of equilibration); focus on the point of the experiments (whatt hypothesis was tested) and what the results are.  committee members are going to be less interested in the details than the intellectual framework being used.
  \begin{figure}[!htb]
      \centering
      \begin{subfigure}{.325\textwidth}
              \centering
              \vspace{0.5cm}
              \includegraphics[width=\textwidth]{NaGA3C11_wedge.eps}
              \vspace{0.05cm}
              \caption{}~\label{fig:monomer}
      \end{subfigure}
%      \begin{subfigure}{.3\textwidth}
%              \centering
%              \includegraphics[width=\textwidth]{monomer_twocolor.pdf}
%              \caption{}~\label{fig:atomistic_monomer}
%      \end{subfigure}
%      \begin{subfigure}{0.3\linewidth}
%              \centering
%              \includegraphics[width=0.6\textwidth]{wedge_thick.pdf}
%              \caption{}~\label{fig:wedge}
%      \end{subfigure}
              \begin{subfigure}{0.325\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{columns.pdf}
              \caption{}~\label{fig:wedge_layer}
      \end{subfigure}
      \begin{subfigure}{0.325\linewidth}
              \centering
              \includegraphics[width=0.6\textwidth]{hexagonal_packing.pdf}
              \caption{}~\label{fig:hex_packing_simple}
      \end{subfigure}
      \caption{(a) The LLC monomer Na-GA3C11 exhibits wedge-like character. (b) 
      Monomers stack on top of each other to create columns with short range order,
      then assemble into pores with hydrophilic head groups (blue) facing towards 
      the pore center. (c) The pores assemble into hexagonally packed columnar
      mesophases.}~\label{fig:assembly}
      \vspace{-0.5cm}
  \end{figure}

@@

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{\textwidth}
  %BJC: probably change this legend to `d = x Angstroms` instead of 
  % disordered/ordered, since I don't have space to talk about ordered / disorderd configurations (requires 
  % nematic order parameter to give a complete justification of the names)
  \includegraphics[width=\textwidth]{regional_density_legend.pdf}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{head_group_density.pdf}
        \caption{Head Groups}
        \label{fig:head_groups_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{tails_density.pdf}
        \caption{Tails}
        \label{fig:tails_regional_density}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
        \includegraphics[width=1\linewidth]{sodium_density.pdf}
        \caption{Sodium Ions}
        \label{fig:sodium_regional_density}
  \end{subfigure}
  %MRS2: important consquence of all radian distribution functions being similar is that we should get useful transport details even if we didn't get the structure exactly right. 
  \caption{In all systems studied, the component radial distribution functions are similar.
      They exhibit a composition gradient transitioning from the hydrophilic to the hydrophobic
          regions. The biggest differences are at r=0 where noise is higher due to
          decreased sampling. The center of the pore is not hollow, but contains sodium ions and
          head groups, even when the system is solvated. This architecture may impede transport in
          the real system in a chemically-dependent manner.
          The solvated system has a lower density of head groups near the
          pore center which is likely due to the swelling that is necessary in order to fit water
          molecules in the pore region.}~\label{fig:overlaid_densities}
  \vspace{-0.5cm}
  \end{figure}

  \noindent \textbf{\large Objective 2:} \textit{\large Determine transport mechanisms} (\textcolor{green!40!olive}{\textbf{Complete}})
  %MRS2: put at the beginning it's been submitted.

@@

  \begin{wrapfigure}{l}{0.65\textwidth}
  \centering
  \vspace{-0.4cm}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{component_density_dry.pdf}
%  %BJC: simulation is extended to smooth out these curves
%  \caption{Dry System}\label{fig:component_density_dry}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \vspace{-0.5cm}
%  \includegraphics[width=\textwidth]{monomer_color_coded.pdf}
%  \label{fig:monomer_color_coded}
%  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{component_density_5wt.pdf}
  \caption{5 wt\% water}\label{fig:component_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.49\linewidth}
  \includegraphics[width=\linewidth]{component_density_10wt.pdf}
  \caption{10 wt\% water}\label{fig:component_density_10wt}
  \end{subfigure}
  \caption{The radial densities of various monomer components paint a
  picture of the pore topology where the pore centers are primarily composed
  of water and sodium ions. 
  %MRS2: there's actually a lot of head groups in the pores except at the very center.  Does the sentence above
  %MRS2: communicate that well? 
The monomer groups labeled in each plot correspond to
  the color-coded monomer pictured in Figure~\ref{fig:HII_mon}. All RDFs
  represent the number of atoms located at a given distance from the pore center
  normalized by the volume of the annular bin to which they belong. The black
  dashed lines are positioned so that they intersect with the maximum head group
  density. (a) In the 5 wt \% system, monomer head groups are situated about 0.45 nm
  from the pore center. Sodium and water are densest near the pore center 
  (b) Monomers in the 10 wt \% system retreat an additional 0.2 nm to make room
  for more water. Water is densest at the pore center, but sodium ion density
  peaks closer to the head groups since many stay bound to carboxylate groups.}\label{fig:component_densities}
  \vspace{-0.75cm}
  \end{wrapfigure}

@@

  The pores of the H\textsubscript{II} phase are primarily a mixture of 
  water and sodium ions. The maximum density of head groups occurs 0.45
  and 0.65 nm from the pore center in the 5 and 10 wt\% water systems 
  respectively (see Figure~\ref{fig:component_densities}). There are 
  almost no head groups occupying the pore center.
  %MRS2: I guess that's not entirely clear to me. Yes, at R=0, but most of the pore volume is at R=0.2-0.4, and there are a lot of head groups there.  There might be a general issue of confusion between ``pore center'' and ``pore regions''

@@

  % BJC: do you think I can get away with an appendix with the solute table + abbreviations that
  % doesn't count towards the page limit?
  %MRS2: not sure.  I think there are ways to clear ou space (see above)
  %MRS2: not great thesis statement.  Thesis statements should be trying to convince reader - this is just listing something you did. 
  We observed transport of 20 different small polar solutes in the pores of
  our model. We created a separate initial configuration for each solute 
  studied and placed 6 solutes, equally spaced in $z$, in each nanopore.
  After a 5 ns equilibration, we allowed the solutes to simulate for
  1 microsecond.

@@

  I have developed a procedure that can build both Ia3d and Pn3m unit cells.
  To our knowledge, nobody has ever built an atomistic bicontinuous cubic 
  phase system without the aid of self-assembly. Self-assembly can be a long
  process, especially for fully atomistic systems. 
  %MRS2: nobody has built an atomistic model, I think - the self-assembly were for very GC models.
  Instead, we used known
  %MRS2: may want to emphasize that for atomistic models, ``long'' is probably at least 2 orders of magnitude longer than our simulations (which are already long)
  analytical equations that describe the surface of these systems in order 
  to place monomers into a unit cell. Monomers are placed perpendicular to
  the surface in random locations that don't overlap. One can control the 
  pore size by translating monomers perpendicular to the surface at the 
  point where they are attached.

@@

  %MRS2: emphasize comparison to experiments more here, based on what they have done, and what they will do; outline how you will compare to those experiments.

%BJC: not sure how much more detail to include. Can go into a lot. Have to expand box and slowly compress. Add glycerol iteratively until there are no gaps.
%MRS2: details of how are not that important; focus on what experiments you will do and why.
